### 2020-04-28 conference_101719.tex
added title and author info

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{A review on Generative Learning in Computer Vision}

\author{\IEEEauthorblockN{Pathan Faisal Khan}
\IEEEauthorblockA{Letterkenny Institute of Technology \\
Port Road, Letterkenny\\
Co. Donegal, Ireland \\
L00151142@student.lyit.ie}}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2020-05-02 paper.tex
renamed files
added intro

--- 2020-04-28 conference_101719.tex
@@
 \begin{abstract}
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
+
 \end{abstract}
@@
 \section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
+Artificial intelligence has made it possible for computers to learn from experiences and perform simple tasks which a human can easily do.
+Visual perception by human-like object recognizing abilities is once such task which scientists have been able to teach computers.
+The field of teaching computers to percieve its environment is called as computer vision.
+
+In the past few years due to advancement and innovation in computing power especially unlocking GPU based distributed computing, computer scientists have achieved good success in able to teach computers to do complex tasks beyond classification like object detection, image segmentation, and object tracking.
 

### 2020-05-03 paper.tex
update

@@
 \documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
 \usepackage{cite}
@@
 Visual perception by human-like object recognizing abilities is once such task which scientists have been able to teach computers.
-The field of teaching computers to percieve its environment is called as computer vision.
+The field of teaching computers to percieve its environment is called as Computer Vision (CV).
 
-In the past few years due to advancement and innovation in computing power especially unlocking GPU based distributed computing, computer scientists have achieved good success in able to teach computers to do complex tasks beyond classification like object detection, image segmentation, and object tracking.
+In the past few years due to advancement and innovation in computing power especially unlocking GPU based distributed computing, computer scientists have achieved good success in able to teach computers to do complex tasks beyond classification like object detection, image segmentation, object tracking, and event detection.
+CV has since been used in numerous ways ranging from automated cars to quality check at factories which usually required an expert to manually check the production line.
+
+In 2014, Goodfellow et al. published a paper on Generative Adversarial Networks (GANs) \cite{b1}. GANs has then been applied in numerous field
 
@@
 
-\section*{Acknowledgment}
+\begin{thebibliography}{00}
+\bibitem{b1} Goodfellow, I.J., Pouget-Abadie, J., Mirza, M., Xu, B., Warde-Farley, D., Ozair, S., Courville, A., Bengio, Y., 2014. Generative Adversarial Networks. arXiv:1406.2661 [cs, stat].
 
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
-
-\section*{References}
-
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
-
-\begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
 \end{thebibliography}
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
-
 \end{document}

### 2020-05-04 paper.tex
completed intro

@@
 
-In 2014, Goodfellow et al. published a paper on Generative Adversarial Networks (GANs) \cite{b1}. GANs has then been applied in numerous field
+In 2014, Goodfellow et al.
+published a paper on Generative Adversarial Networks (GANs) \cite{b1}.
+GANs has since then been applied in numerous fields including Natural Language Processing (NLP) and computer vision.
+This family of deep learning methods has become quite popular due to its good results.
+In this review paper provides a survey on recent adaptations of GAN alongwith the first-original version often called as vanilla GAN.
 
-\section{Ease of Use}
+The rest of the paper is organized as follows-- Section \ref{lr} will provide an overview of generative learning.
+Section \ref{techniques} will cover recent techniques used for generative learning.
+Section \ref{comparison} will provide a comparison of different techniques discussed in section \ref{techniques}.
+Finally, section \ref{conclusion} will provide some remarks to conclude the paper.
 
-\subsection{Maintaining the Integrity of the Specifications}
+\section{Literature Review}
+\label{lr}
 
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
+\section{Techniques}
+\label{techniques}
 
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-proofreading, spelling and grammar.
+\section{Comparison}
+\label{comparison}
 
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
-
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
-
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
-
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
-
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
-
-\begin{figure}[htbp]
-\centerline{\includegraphics{fig1.png}}
-\caption{Example of a figure caption.}
-\label{fig}
-\end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
+\section{Conclusion}
+\label{conclusion}
 

### 2020-05-04 paper.tex
update intro and started lit review

@@
 
-In 2014, Goodfellow et al.
-published a paper on Generative Adversarial Networks (GANs) \cite{b1}.
-GANs has since then been applied in numerous fields including Natural Language Processing (NLP) and computer vision.
-This family of deep learning methods has become quite popular due to its good results.
-In this review paper provides a survey on recent adaptations of GAN alongwith the first-original version often called as vanilla GAN.
+With such advancements, the need for data is never ending.
+CV models running on neural networks require huge amount labeled training data to train them.
+But the problem lies in finding suitable high-quality data.
+Manual scavenging and labelling of data is not an ideal approach as it is costly to do so.
+The only option left for computer scientists is to produce high quality artificial data either from scratch or by manipulating existing data.
+Generative learning is one such popular way to generate artificial data.
+In this paper, we will look at different generative methods introduced lately.
 
@@
 \label{lr}
+In 2014, Goodfellow et al.
+published a paper on Generative Adversarial Networks (GANs) \cite{b1}.
+GANs has since then been applied in numerous fields including Natural Language Processing (NLP) and computer vision.
+This family of deep learning methods has become quite popular due to its good results.
+In this review paper provides a survey on recent adaptations of GAN alongwith the first-original version often called as vanilla GAN.
 

### 2020-05-05 paper.tex
added background

@@
 \usepackage{xcolor}
+\usepackage{multirow}
+\usepackage{booktabs}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 \begin{abstract}
-
+Artificial intelligence has made it possible for computers to learn from experiences and perform simple tasks which a human can easily do.
+Visual perception by human-like object recognizing abilities is once such task which scientists have been able to teach computers.
+In the past few years due to advancement and innovation in computing power especially unlocking GPU based distributed computing, computer scientists have achieved good success in able to teach computers to do complex tasks beyond classification like object detection, image segmentation, object tracking, and event detection.
+Computer Vision (CV) has since been used in numerous ways ranging from automated cars to quality check at factories which usually required an expert to manually check the production line.Artificial intelligence has made it possible for computers to learn from experiences and perform simple tasks which a human can easily do.
+Visual perception by human-like object recognizing abilities is once such task which scientists have been able to teach computers.
+In the past few years due to advancement and innovation in computing power especially unlocking GPU based distributed computing, computer scientists have achieved good success in able to teach computers to do complex tasks beyond classification like object detection, image segmentation, object tracking, and event detection.
 \end{abstract}
@@
 Visual perception by human-like object recognizing abilities is once such task which scientists have been able to teach computers.
-The field of teaching computers to percieve its environment is called as Computer Vision (CV).
-
 In the past few years due to advancement and innovation in computing power especially unlocking GPU based distributed computing, computer scientists have achieved good success in able to teach computers to do complex tasks beyond classification like object detection, image segmentation, object tracking, and event detection.
-CV has since been used in numerous ways ranging from automated cars to quality check at factories which usually required an expert to manually check the production line.
+Computer Vision (CV) has since been used in numerous ways ranging from automated cars to quality check at factories which usually required an expert to manually check the production line.
 
@@
 Generative learning is one such popular way to generate artificial data.
-In this paper, we will look at different generative methods introduced lately.
+This paper will look at different generative methods introduced lately.
 
@@
 
-\section{Literature Review}
+\section{Generative Learning}
 \label{lr}
+\subsection{Background}
+Computer scientists has contributed a lot of research towards generating synthetic visual data.
+With such techniques, computer scientists has been able to generate data which is almost indistinguishable by a human eye.
+This fast availibility of generated data has made it possible to solve a lot of modern problems in deep learning.
+
+There has been some generative techniques around in this field of deep learning.
 In 2014, Goodfellow et al.
 published a paper on Generative Adversarial Networks (GANs) \cite{b1}.
+This state-of-the-art technique proved to be a major break-through in deep learning especially in CV.
 GANs has since then been applied in numerous fields including Natural Language Processing (NLP) and computer vision.
 This family of deep learning methods has become quite popular due to its good results.
-In this review paper provides a survey on recent adaptations of GAN alongwith the first-original version often called as vanilla GAN.
+This review paper provides a survey on recent adaptations of GAN alongwith the first-original version often called as vanilla GAN.
+Autoencoders is a class of unsupervised neural networks which is also a popular method to generate data with some applications dating back to the 80s \cite{b2, b3}.
+Variational Autoencoders (VAEs) in specific is a generative technique.
+
+\subsection{Taxonomy}
+The following Table \ref{tab:taxonomy_table} presents taxonomy of different generative learning techniques--
+
+\begin{table*}[]
+    \caption{Taxonomy and citations of Generative Learning techniques}
+    \label{tab:taxonomy_table}
+    \centering
+    \begin{tabular}{l l l}
+        \toprule
+        \multicolumn{2}{l}{Technique} & Citations \\ 
+        \midrule
+
+        \multirow{2}{*}{} & Parallel Breadth-First Search & \begin{tabular}[c]{@{}l@{}} \cite{b1}\\
+            \cite{b1}   \\
+            \cite{b1}   \\
+        \end{tabular}\\ 
+        \cline{2-3} 
+        \multirow{2}{*}{} & Parallel Depth-First Search & \begin{tabular}[c]{@{}l@{}} \cite{b1}\\
+            \cite{b1}   \\
+            \cite{b1}   \\
+        \end{tabular}\\ 
+        \cline{2-3} 
+        \multirow{2}{*}{} & Single-Source Shortest Path & \begin{tabular}[c]{@{}l@{}} \cite{b1}\\
+            \cite{b1}   \\
+            \cite{b1}   \\
+        \end{tabular}\\  
+        \cline{2-3} 
+        Generative Adversarial Networks &  All-Pairs Shortest Path  & \begin{tabular}[c]{@{}l@{}} \cite{b1}\\
+            \cite{b1,b1}   \\
+            \cite{b1, b1}   \\
+        \end{tabular}\\ 
+        \cline{2-3} 
+        \multirow{2}{*}{} & Minimum Weight Spanning Tree & \begin{tabular}[c]{@{}l@{}} \cite{b1, b1}\\
+            \cite{b1, b1}   \\
+            \cite{b1, b1}   \\
+        \end{tabular}\\ 
+        \cline{2-3} 
+        \multirow{2}{*}{} & Random Walk & \begin{tabular}[c]{@{}l@{}} \cite{b1, b1}\\
+            \cite{b1, b1}   \\
+            \cite{b1}   \\
+        \end{tabular}\\  
+        \midrule
+
+        \multirow{2}{*}{} & Label Propagation & \cite{b1}\\ 
+        \cline{2-3} 
+        \multirow{2}{*}{} & Louvain Modularity & \begin{tabular}[c]{@{}l@{}} \cite{b1, b1}\\
+            \cite{b1, b1}   \\
+            \cite{b1} \\
+        \end{tabular}\\ 
+        \cline{2-3} 
+        Autoencoders & Node Clustering Coefficient and Average Clustering Coefficient & \cite{b1}   \\ 
+        \cline{2-3}
+        \multirow{2}{*}{} & Bron-Kerbosch & \begin{tabular}[c]{@{}l@{}} \cite{b1}\\
+            \cite{b1}   \\
+        \end{tabular}\\
+
+        \bottomrule
+    \end{tabular}
+\end{table*}
 
@@
 
+\bibitem{b2} Ballard, D.H., 1987.
+Modular learning in neural networks, in: Proceedings of the Sixth National Conference on Artificial Intelligence - Volume 1, AAAI’87.
+AAAI Press, Seattle, Washington, pp.
+279–284.
+
+\bibitem{b3} Rumelhart, D.E., Hinton, G.E., Williams, R.J., 1986.
+Learning internal representations by error propagation, in: Parallel Distributed Processing: Explorations in the Microstructure of Cognition, Vol.
+1: Foundations.
+MIT Press, Cambridge, MA, USA, pp.
+318–362.
+
 \end{thebibliography}

### 2020-05-05 paper.tex
update

@@
 
-        \multirow{2}{*}{} & Parallel Breadth-First Search & \begin{tabular}[c]{@{}l@{}} \cite{b1}\\
-            \cite{b1}   \\
-            \cite{b1}   \\
+        \multirow{2}{*}{} & Vanilla GAN & \begin{tabular}[c]{@{}l@{}} \cite{b1}\\
         \end{tabular}\\
+
         \cline{2-3} 
-        \multirow{2}{*}{} & Parallel Depth-First Search & \begin{tabular}[c]{@{}l@{}} \cite{b1}\\
-            \cite{b1}   \\
-            \cite{b1}   \\
+        \multirow{2}{*}{} & Conditional GANs & \begin{tabular}[c]{@{}l@{}} \cite{b4}\\
         \end{tabular}\\
+
         \cline{2-3} 
-        \multirow{2}{*}{} & Single-Source Shortest Path & \begin{tabular}[c]{@{}l@{}} \cite{b1}\\
-            \cite{b1}   \\
-            \cite{b1}   \\
+        \multirow{2}{*}{} & Progressive GANs & \begin{tabular}[c]{@{}l@{}} \cite{b12}\\
         \end{tabular}\\
+
         \cline{2-3} 
-        Generative Adversarial Networks &  All-Pairs Shortest Path  & \begin{tabular}[c]{@{}l@{}} \cite{b1}\\
-            \cite{b1,b1}   \\
-            \cite{b1, b1}   \\
+        \multirow{2}{*}{} & Deep Convolutional GANs (DCGANs) & \begin{tabular}[c]{@{}l@{}} \cite{b5}\\
         \end{tabular}\\
+
         \cline{2-3} 
-        \multirow{2}{*}{} & Minimum Weight Spanning Tree & \begin{tabular}[c]{@{}l@{}} \cite{b1, b1}\\
-            \cite{b1, b1}   \\
-            \cite{b1, b1}   \\
+        \multirow{2}{*}{} & Auxiliary Classifier GANs & \begin{tabular}[c]{@{}l@{}} \cite{b7}\\
         \end{tabular}\\
+
         \cline{2-3} 
-        \multirow{2}{*}{} & Random Walk & \begin{tabular}[c]{@{}l@{}} \cite{b1, b1}\\
-            \cite{b1, b1}   \\
-            \cite{b1}   \\
+        \multirow{2}{*}{} & 3D-GAN & \begin{tabular}[c]{@{}l@{}} \cite{b8}\\
         \end{tabular}\\
+
+        \cline{2-3} 
+        Generative Adversarial Networks &  Info GANs  & \begin{tabular}[c]{@{}l@{}} \cite{b6}\\
+        \end{tabular}\\
+
+        \cline{2-3} 
+        \multirow{2}{*}{} & PacGAN & \begin{tabular}[c]{@{}l@{}} \cite{b9}\\
+        \end{tabular}\\
+
+        \cline{2-3} 
+        \multirow{2}{*}{} & Pix2PixGAN & \begin{tabular}[c]{@{}l@{}} \cite{b10}\\
+        \end{tabular}\\
+
+        \cline{2-3} 
+        \multirow{2}{*}{} & Cycle-GAN & \begin{tabular}[c]{@{}l@{}} \cite{b11}\\
+        \end{tabular}\\
+
+        \cline{2-3} 
+        \multirow{2}{*}{} & Text-to-Image Synthesis (StackGAN) & \begin{tabular}[c]{@{}l@{}} \cite{b13}\\
+        \end{tabular}\\
+
+        \cline{2-3} 
+        \multirow{2}{*}{} & Super-Resolution GAN & \begin{tabular}[c]{@{}l@{}} \cite{b14}\\
+        \end{tabular}\\
+
         \midrule
@@
 
+\bibitem{b4} Mirza, M., Osindero, S., 2014. Conditional Generative Adversarial Nets. arXiv:1411.1784 [cs, stat].
+
+\bibitem{b5} Radford, A., Metz, L., Chintala, S., 2016. Unsupervised Representation Learning with Deep Convolutional Generative Adversarial Networks. arXiv:1511.06434 [cs].
+
+\bibitem{b6} Chen, X., Duan, Y., Houthooft, R., Schulman, J., Sutskever, I., Abbeel, P., 2016.
+InfoGAN: Interpretable Representation Learning by Information Maximizing Generative Adversarial Nets.
+arXiv:1606.03657 [cs, stat].
+
+\bibitem{b7} Odena, A., Olah, C., Shlens, J., 2017. Conditional Image Synthesis With Auxiliary Classifier GANs. arXiv:1610.09585 [cs, stat].
+
+\bibitem{b8} Wu, J., Zhang, C., Xue, T., Freeman, W.T., Tenenbaum, J.B., 2016. Learning a Probabilistic Latent Space of Object Shapes via 3D Generative-Adversarial Modeling.
+
+\bibitem{b9} Lin, Z., Khetan, A., Fanti, G., Oh, S., 2018.
+PacGAN: The power of two samples in generative adversarial networks, in: Bengio, S., Wallach, H., Larochelle, H., Grauman, K., Cesa-Bianchi, N., Garnett, R.
+(Eds.), Advances in Neural Information Processing Systems 31.
+Curran Associates, Inc., pp.
+1498–1507.
+
+\bibitem{b10} Isola, P., Zhu, J.-Y., Zhou, T., Efros, A.A., 2018. Image-to-Image Translation with Conditional Adversarial Networks. arXiv:1611.07004 [cs].
+
+\bibitem{b11} Zhu, J.-Y., Park, T., Isola, P., Efros, A.A., 2018. Unpaired Image-to-Image Translation using Cycle-Consistent Adversarial Networks. arXiv:1703.10593 [cs].
+
+\bibitem{b12} Karras, T., Aila, T., Laine, S., Lehtinen, J., 2018. Progressive Growing of GANs for Improved Quality, Stability, and Variation. arXiv:1710.10196 [cs, stat].
+
+\bibitem{b13} Zhang, H., Xu, T., Li, H., Zhang, S., Wang, X., Huang, X., Metaxas, D., 2017.
+StackGAN: Text to Photo-realistic Image Synthesis with Stacked Generative Adversarial Networks.
+arXiv:1612.03242 [cs, stat].
+
+\bibitem{b14} Ledig, C., Theis, L., Huszar, F., Caballero, J., Cunningham, A., Acosta, A., Aitken, A., Tejani, A., Totz, J., Wang, Z., Shi, W., 2017.
+Photo-Realistic Single Image Super-Resolution Using a Generative Adversarial Network.
+arXiv:1609.04802 [cs, stat].
+
 \end{thebibliography}

### 2020-05-07 paper.tex
done with taxonomy
added description for GAN

@@
         \cline{2-3} 
-        \multirow{2}{*}{} & Conditional GANs & \begin{tabular}[c]{@{}l@{}} \cite{b4}\\
+        \multirow{2}{*}{} & Conditional GAN & \begin{tabular}[c]{@{}l@{}} \cite{b4}\\
         \end{tabular}\\
@@
         \cline{2-3} 
-        \multirow{2}{*}{} & Progressive GANs & \begin{tabular}[c]{@{}l@{}} \cite{b12}\\
+        \multirow{2}{*}{} & Progressive GAN & \begin{tabular}[c]{@{}l@{}} \cite{b12}\\
         \end{tabular}\\
@@
         \cline{2-3} 
-        \multirow{2}{*}{} & Deep Convolutional GANs (DCGANs) & \begin{tabular}[c]{@{}l@{}} \cite{b5}\\
+        \multirow{2}{*}{} & Deep Convolutional GANs (DCGAN) & \begin{tabular}[c]{@{}l@{}} \cite{b5}\\
         \end{tabular}\\
@@
         \cline{2-3} 
-        \multirow{2}{*}{} & Auxiliary Classifier GANs & \begin{tabular}[c]{@{}l@{}} \cite{b7}\\
+        \multirow{2}{*}{} & Auxiliary Classifier GAN & \begin{tabular}[c]{@{}l@{}} \cite{b7}\\
         \end{tabular}\\
@@
 
-        \multirow{2}{*}{} & Label Propagation & \cite{b1}\\ 
-        \cline{2-3} 
-        \multirow{2}{*}{} & Louvain Modularity & \begin{tabular}[c]{@{}l@{}} \cite{b1, b1}\\
-            \cite{b1, b1}   \\
-            \cite{b1} \\
-        \end{tabular}\\ 
-        \cline{2-3} 
-        Autoencoders & Node Clustering Coefficient and Average Clustering Coefficient & \cite{b1}   \\ 
-        \cline{2-3}
-        \multirow{2}{*}{} & Bron-Kerbosch & \begin{tabular}[c]{@{}l@{}} \cite{b1}\\
-            \cite{b1}   \\
-        \end{tabular}\\
+        Autoencoders & Variational Autoencoders (VAEs) & \cite{b15}   \\
 
@@
 \label{techniques}
+
+\subsection{Generative Adversarial Networks (GANs)}
+Goodfellow et al.
+developed this state-of-the-art class of neural networks with two key components; a generator and a discriminator.
+The generator is a neural network which takes a random vector input usually a noise and generates a new plausible output out of it in the domain.
+This vector input is taken from a Gaussian distribution.
+A Gaussian or normal distribution is a probability distribution around a mean, which signifies the data around the mean is more frequent as compared to data points away from the mean.
+A Gaussian distribution shows a bell curve when plotted.
+The vector is referred as a latent space which means significant variables but not explicity visible.
+Due to the fact that it uses random vector sample every time, the model becomes stochastic, the output will be non-deterministic every time.
+The generator makes unlimited samples out of it.
+The discriminator, a classification model, then takes input from the training dataset as well as output from the generator model and attempts to identify source of the input, whether it is from the training dataset or from the generator generated ouput.
+Both models are meant to compete with each other, the generator has to fool the discriminator into incorrectly classifying its sample as a real sample from the training set and the discriminator has to make itself perfect in correctly classifying input samples.
+The generator and the discriminator are both trained alongwith.
+When the discriminator predicts the class of the input sample, it is tweaked to perform better for the next sample, likewise the generator is updated to create samples which will fool the discriminator.
+Even though GAN is an unsupervised learning technique but this architecture of it is designed as a supervised learning technique.
+
+The following sections cover some variants of GAN:
+
+\begin{figure}[h]
+    \centerline{\includegraphics[scale=0.8]{figures/generator.pdf}}
+    \caption{The numbers depict the order of traversal of nodes in a BFS implementation}
+    \label{fig1}
+\end{figure}
+
+\subsubsection{Vanilla GAN}
+
+\subsubsection{Conditional GAN}
+
+\subsubsection{Progressive GAN}
+
+\subsubsection{Deep Convolutional GAN (DCGAN)}
+
+\subsubsection{Auxiliary Classifier GAN}
+
+\subsubsection{3D-GAN}
+
+\subsubsection{Info GAN}
+
+\subsubsection{PacGAN}
+
+\subsubsection{Pix2PixGAN}
+
+\subsubsection{Cycle-GAN}
+
+\subsubsection{Text-to-Image Synthesis (StackGAN)}
+
+\subsubsection{Super-Resolution GAN}
+
+\subsection{Autoencoders}
+
+\subsubsection{Variational Autoencoders (VAEs)}
 
@@
 
+\bibitem{b15} Doersch, C., 2016. Tutorial on Variational Autoencoders. arXiv:1606.05908 [cs, stat].
+
 \end{thebibliography}

### 2020-05-07 paper.tex
removed figure
added GAN and CGAN diagrams

@@
 
-        \multirow{2}{*}{} & Vanilla GAN & \begin{tabular}[c]{@{}l@{}} \cite{b1}\\
-        \end{tabular}\\
-
-        \cline{2-3} 
         \multirow{2}{*}{} & Conditional GAN & \begin{tabular}[c]{@{}l@{}} \cite{b4}\\
@@
         \cline{2-3} 
-        \multirow{2}{*}{} & 3D-GAN & \begin{tabular}[c]{@{}l@{}} \cite{b8}\\
+        Generative Adversarial Networks &  Info GANs  & \begin{tabular}[c]{@{}l@{}} \cite{b6}\\
         \end{tabular}\\
@@
         \cline{2-3} 
-        Generative Adversarial Networks &  Info GANs  & \begin{tabular}[c]{@{}l@{}} \cite{b6}\\
+        \multirow{2}{*}{} & 3D-GAN & \begin{tabular}[c]{@{}l@{}} \cite{b8}\\
         \end{tabular}\\
@@
 Even though GAN is an unsupervised learning technique but this architecture of it is designed as a supervised learning technique.
+The generator model is then used discarding the discriminator model.
 
-The following sections cover some variants of GAN:
+The following figure \ref{fig1} describes the working of a GAN.
 
-\begin{figure}[h]
-    \centerline{\includegraphics[scale=0.8]{figures/generator.pdf}}
-    \caption{The numbers depict the order of traversal of nodes in a BFS implementation}
+\begin{figure}[!h]
+    \centerline{\includegraphics[scale=0.6]{figures/GAN.pdf}}
+    \caption{End-to-end process of the Vanilla GAN}
     \label{fig1}
@@
 
-\subsubsection{Vanilla GAN}
+\subsubsection{Conditional GAN}
+Conditional GAN is an extension of GAN proposed by Mirza et al.
+in 2014 \cite{b4}.
+It works on the principal of conditional probability which is defined as the probability of an event given another event mathematically represented as $P(A|B)$ which translates to probability of $A$ given $B$.
+Conditional GAN is conditioned using extra information which is passed to the generator as well as to the discriminator.
+This extra information can be any supplementary information like image labels.
+The discriminator gets the extra information alongwith the input from generator.
 
-\subsubsection{Conditional GAN}
+The following figure \ref{fig2} describes the working of a conditional GAN.
+
+\begin{figure}[!h]
+    \centerline{\includegraphics[scale=0.6]{figures/CGAN.pdf}}
+    \caption{End-to-end process of the conditional GAN}
+    \label{fig2}
+\end{figure}
 

### 2020-05-07 paper.tex
done with CGAN

@@
 \begin{abstract}
-Artificial intelligence has made it possible for computers to learn from experiences and perform simple tasks which a human can easily do.
-Visual perception by human-like object recognizing abilities is once such task which scientists have been able to teach computers.
-In the past few years due to advancement and innovation in computing power especially unlocking GPU based distributed computing, computer scientists have achieved good success in able to teach computers to do complex tasks beyond classification like object detection, image segmentation, object tracking, and event detection.
-Computer Vision (CV) has since been used in numerous ways ranging from automated cars to quality check at factories which usually required an expert to manually check the production line.Artificial intelligence has made it possible for computers to learn from experiences and perform simple tasks which a human can easily do.
-Visual perception by human-like object recognizing abilities is once such task which scientists have been able to teach computers.
-In the past few years due to advancement and innovation in computing power especially unlocking GPU based distributed computing, computer scientists have achieved good success in able to teach computers to do complex tasks beyond classification like object detection, image segmentation, object tracking, and event detection.
+
 \end{abstract}
@@
 The generator model is then used discarding the discriminator model.
-
 The following figure \ref{fig1} describes the working of a GAN.
@@
 The discriminator gets the extra information alongwith the input from generator.
-
+One of the applications of conditional GAN is generating image of a person given its gender.
 The following figure \ref{fig2} describes the working of a conditional GAN.

### 2020-05-07 paper.tex
added pgan

@@
 \subsubsection{Progressive GAN}
+Karras et al in 2017 published a paper introducing progressive GAN \cite{b12}.
+According to the authors of the paper, they proposed a novel training technique where the generator and discriminator grow progressively as they train themselves.
+Growing progressively means adding more layers to themselves to fine tune the model.
+With this approach, the training time decreases.
+The generator produces low quality images and as more layers are added it fine tunes the model resulting in high quality images.
+This progressive learning technique allows the model to gradually discover large scale composition of the image and then focus on improving the fine details of the image.
+New layers are added in such a way that it does not drastically affect the fine tuned network.
+Figure \ref{fig3} shows how layers are added to both the generator and discriminator together.
+
+\begin{figure}[!h]
+    \centerline{\includegraphics[scale=0.7]{figures/PGAN.pdf}}
+    \caption{Addition of layers in every iteration of progressive GAN}
+    \label{fig3}
+\end{figure}
 

### 2020-05-07 paper.tex
added dcgan

@@
 \subsubsection{Deep Convolutional GAN (DCGAN)}
+Deep Convolutional GAN (DCGAN), one of the first convolutional GANs proposed by Radford et al in early 2016 \cite{b5}, relies on the architecture of CNN.
+The authors proposed a few architecture guidelines which describes the composition of a DCGAN.
+They have taken a CNN and replaced the pooling layers with convolutions with fractional-strides in the generator in order to reduce feature maps resulting from the sample Gaussian input.
+They also have replaced the pooling layers in discriminator with convolutions with strides resulting in more parameters to train the model.
+They then used batch normalization for both the models resulting in stable training.
+Then to lower the training parameters, they removed hidden layers.
+Then finally they have used ReLU and LeakyReLU as the activation function in the generator and the discriminator respectively.
 

### 2020-05-07 paper.tex
added acgan

@@
 \subsubsection{Auxiliary Classifier GAN}
+Auxiliary classifier GAN (ACGAN), proposed by Odena et al in 2017 \cite{b7}, is able to generate high-resolution images using a technique called label conditioning.
+At that time, the experiment resulted in images of 128 x 128 resolution images.
+They also were able to identify the collapsing behavior of a GAN.
+The model the presented is a conditional model which was able to took a lot of lables/classes as supplementary input.
+They were able to create highly different sample spaces at a time.
+Unlike CGAN, the discriminator in this case learnt the supplementary information on its own, this technique is referred as reconstruction loss.
 

### 2020-05-08 paper.tex
added 3dgan

@@
 \subsubsection{3D-GAN}
+3D-GAN, is a 3D-object generation GAN proposed by Wu et al \cite{b8} in 2016.
+This was a novel technique which focused on the 3D space generation using GAN using CNN.
+3D object generation is not an easy task due to the high-dimensionality of the object.
+With high dimensionality, a large number of parameters are needed.
+To solve this high dimensionality problem, CNN is the best bet out there.
+A CNN with the apropriate configuration helps in increasing the dimensions of the sample space while also being able to reduce the parameters/features.
+The authors proposed a CNN which is similar to DCGAN.
+With this architecture they have managed to reduce the features by a great amount.
+They added a Sigmoid layer in the end.
+Due to the fact that it is difficult to generate a 3D object as compared to be able to classify them, the authors had to come up with a simple training method.
+They used a bigger batch with very low learning rate.
+This method proved to be able to generate good-quality shapes.
 

### 2020-05-08 paper.tex
added vae

@@
 \subsection{Autoencoders}
+Autoencoders are a type of neural networks which learns in an unsupervised way.
+As the name suggests, it encodes the input and then try to reconstruct the input to generate a similar or better output.
+This way it learns to reduce unnecassary features while being able to produce the same input data it was fed.
+This technique is often used for dimension reduction, fix noisy data, or compression without losing significant parts of the data.
+Autoencoders generally use a feedforward architecture which uses backpropagation while training.
+
+\begin{figure}[!h]
+    \centerline{\includegraphics[scale=0.6]{figures/AE.pdf}}
+    \caption{Architecture of an autoencoder}
+    \label{fig4}
+\end{figure}
+
+In the above figure \ref{fig4}, an autencoder is shown.
+It has 2 main components: an encoder which takes in the input and encodes it and a decoder which uses the encoded output of the encoder as input and tries to generate the original input of the model.
+Due to the backpropagation nature of this model, the training is quite fast.
 
 \subsubsection{Variational Autoencoders (VAEs)}
+Variational Autoencoders (VAEs) are generative models.
+It is based on vanilla autencoders but with a distinct property of picking up input from a latent space which is continous in nature.
+It basically avoids overfitting by regularizing its training.
+Unlike GAN, where a discriminator is used to classify the data which in turn helps the generator to tune itself to fool the discriminator, VAEs learn how to generate the data.
+The model first encodes the input over the latent space as distribution, then it picks up a point from the resultant latent space and then decoded.
+The error in decoding is calculated and backpropagated in the network.
+It uses Stochastic Gradient descent to train itself.
+This enables the model to generate distinct samples with similar characteristics to the input.
+VAEs can work with an surprisingly diverse data forms, continous or discrete, labelled or unlabelled, sequential or non-sequential, making it an extremely efficient generative learning technique.
+VAEs has proven to produce images out of latent space but it often performs poorly.
+This is the reason why VAEs are not used anymore for generative learning in computer vision.
 

### 2020-05-08 paper.tex
added InfoGAN

@@
 
-\subsubsection{Info GAN}
+\subsubsection{InfoGAN}
+InfoGAN was proposed by Chen et al in 2016 \cite{b6}.
+InfoGAN is a GAN which utilises the information shared among a subset of the latent space.
+It also uses an unsupervised learning technique called disentagled representation which allocated different sets of dimensions by breaking down features of the data.
+Disentangled information represents a low representation of the data.
+With the introdcution of this technique, it makes the model to be truly unsupervised.
+InfoGAN as claimed by the authors contributes comparatively less computation cost when used with GAN also making it easier to train.
 

### 2020-05-08 paper.tex
added abstract

@@
 \begin{abstract}
-
+Generative learning is the technique to generate artificial data.
+This paper has covered a brief review of different generative learning techniques applied in computer vision to generate visual data.
+With advancement in computing power especially utilisation of GPU for distributed computing, a lot of deep learning techniques has been developed in this field of computer vision.
+Generative Adversarial Networks and autoencoders are such unsupervised deep learning neural networks.
+GANs have garnered a lot of interest by computre scientists due to its high quality image generation and also because of its novel yet simple architecture.
+A lot of variants of GANs are have been developed since the original GAN was introduced by Goodfellow et al in 2014 \cite{b1}.
+These variants have either tweak or have build upon the existing model.
+Some of the techniques covered in this paper are conditional GAN, progressive GAN, deep convolutional GANs, auxiliary GAN, InfoGANs, 3D-GAN, PacGAN, Pix2PixGAN, Cycle-GAN, Text-to-Image Synthesis (StackGAN), and Super-Resolution GAN.
+These models are just a few among others presented by researchers.
+This paper has also provided a brief critique on Variational Autoencoders which is a variant of the autencoder neural network.
 \end{abstract}
@@
 Section \ref{techniques} will cover recent techniques used for generative learning.
-Section \ref{comparison} will provide a comparison of different techniques discussed in section \ref{techniques}.
 Finally, section \ref{conclusion} will provide some remarks to conclude the paper.
@@
 
-\section{Comparison}
-\label{comparison}
-
 \section{Conclusion}

### 2020-05-08 paper.tex
updated keywords

@@
 \begin{IEEEkeywords}
-component, formatting, style, styling, insert
+generative learning, GAN, autoencoder, computer vision, conditional GAN, progressive GAN, deep convolutional GANs, auxiliary GAN, InfoGANs, 3D-GAN, PacGAN, Pix2PixGAN, Cycle-GAN, Text-to-Image Synthesis (StackGAN), Super-Resolution GAN, Variational Autoencoders
 \end{IEEEkeywords}

### 2020-05-08 paper.tex
final

@@
 \begin{abstract}
-Generative learning is the technique to generate artificial data.
+    Generative learning is a technique to generate artificial data.
 This paper has covered a brief review of different generative learning techniques applied in computer vision to generate visual data.
-With advancement in computing power especially utilisation of GPU for distributed computing, a lot of deep learning techniques has been developed in this field of computer vision.
+With the advancement in computing power especially the utilisation of GPU for distributed computing, a lot of deep learning techniques has been developed in this field of computer vision.
 Generative Adversarial Networks and autoencoders are such unsupervised deep learning neural networks.
-GANs have garnered a lot of interest by computre scientists due to its high quality image generation and also because of its novel yet simple architecture.
+GANs have garnered a lot of interest by computer scientists due to its high-quality image generation and also because of its novel yet simple architecture.
 A lot of variants of GANs are have been developed since the original GAN was introduced by Goodfellow et al in 2014 \cite{b1}.
-These variants have either tweak or have build upon the existing model.
+These variants have either tweak or have built upon the existing model.
 Some of the techniques covered in this paper are conditional GAN, progressive GAN, deep convolutional GANs, auxiliary GAN, InfoGANs, 3D-GAN, PacGAN, Pix2PixGAN, Cycle-GAN, Text-to-Image Synthesis (StackGAN), and Super-Resolution GAN.
 These models are just a few among others presented by researchers.
-This paper has also provided a brief critique on Variational Autoencoders which is a variant of the autencoder neural network.
+This paper has also provided a brief critique of Variational Autoencoders which is a variant of the autoencoder neural network.
 \end{abstract}
@@
 Visual perception by human-like object recognizing abilities is once such task which scientists have been able to teach computers.
-In the past few years due to advancement and innovation in computing power especially unlocking GPU based distributed computing, computer scientists have achieved good success in able to teach computers to do complex tasks beyond classification like object detection, image segmentation, object tracking, and event detection.
+In the past few years due to advancement and innovation in computing power especially unlocking GPU based distributed computing, computer scientists have achieved success in able to teach computers to do complex tasks beyond classification like object detection, image segmentation, object tracking, and event detection.
 Computer Vision (CV) has since been used in numerous ways ranging from automated cars to quality check at factories which usually required an expert to manually check the production line.
@@
 \subsection{Background}
-Computer scientists has contributed a lot of research towards generating synthetic visual data.
-With such techniques, computer scientists has been able to generate data which is almost indistinguishable by a human eye.
-This fast availibility of generated data has made it possible to solve a lot of modern problems in deep learning.
+Computer scientists have contributed a lot of research towards generating synthetic visual data.
+With such techniques, computer scientists have been able to generate data which is almost indistinguishable by a human eye.
+This fast availability of generated data has made it possible to solve a lot of modern problems in deep learning.
 
-There has been some generative techniques around in this field of deep learning.
+There have been some generative techniques around in this field of deep learning.
 In 2014, Goodfellow et al.
 published a paper on Generative Adversarial Networks (GANs) \cite{b1}.
-This state-of-the-art technique proved to be a major break-through in deep learning especially in CV.
+This state-of-the-art technique proved to be a major break-through in deep learning, especially in the CV.
 GANs has since then been applied in numerous fields including Natural Language Processing (NLP) and computer vision.
 This family of deep learning methods has become quite popular due to its good results.
-This review paper provides a survey on recent adaptations of GAN alongwith the first-original version often called as vanilla GAN.
+This review paper provides a survey on recent adaptations of GAN along with the first-original version often called as vanilla GAN.
 Autoencoders is a class of unsupervised neural networks which is also a popular method to generate data with some applications dating back to the 80s \cite{b2, b3}.
@@
 A Gaussian distribution shows a bell curve when plotted.
-The vector is referred as a latent space which means significant variables but not explicity visible.
-Due to the fact that it uses random vector sample every time, the model becomes stochastic, the output will be non-deterministic every time.
+The vector is referred to as a latent space which means significant variables but not explicitly visible.
+Since it uses a random vector sample every time, the model becomes stochastic, the output will be non-deterministic every time.
 The generator makes unlimited samples out of it.
-The discriminator, a classification model, then takes input from the training dataset as well as output from the generator model and attempts to identify source of the input, whether it is from the training dataset or from the generator generated ouput.
-Both models are meant to compete with each other, the generator has to fool the discriminator into incorrectly classifying its sample as a real sample from the training set and the discriminator has to make itself perfect in correctly classifying input samples.
-The generator and the discriminator are both trained alongwith.
-When the discriminator predicts the class of the input sample, it is tweaked to perform better for the next sample, likewise the generator is updated to create samples which will fool the discriminator.
+The discriminator, a classification model, then takes input from the training dataset as well as output from the generator model and attempts to identify the source of the input, whether it is from the training dataset or the generator generated output.
+Both models are meant to compete with each other, the generator has to fool the discriminator into incorrectly classifying its sample as a real sample from the training set and the discriminator has to make itself perfect incorrectly classifying input samples.
+The generator and the discriminator are both trained along with.
+When the discriminator predicts the class of the input sample, it is tweaked to perform better for the next sample, likewise, the generator is updated to create samples which will fool the discriminator.
 Even though GAN is an unsupervised learning technique but this architecture of it is designed as a supervised learning technique.
-The generator model is then used discarding the discriminator model.
+The generator model is then used to discarding the discriminator model.
 The following figure \ref{fig1} describes the working of a GAN.
@@
 Deep Convolutional GAN (DCGAN), one of the first convolutional GANs proposed by Radford et al in early 2016 \cite{b5}, relies on the architecture of CNN.
-The authors proposed a few architecture guidelines which describes the composition of a DCGAN.
-They have taken a CNN and replaced the pooling layers with convolutions with fractional-strides in the generator in order to reduce feature maps resulting from the sample Gaussian input.
+The authors proposed a few architecture guidelines which describe the composition of a DCGAN.
+They have taken a CNN and replaced the pooling layers with convolutions with fractional-strides in the generator to reduce feature maps resulting from the sample Gaussian input.
 They also have replaced the pooling layers in discriminator with convolutions with strides resulting in more parameters to train the model.
@@
 They also were able to identify the collapsing behavior of a GAN.
-The model the presented is a conditional model which was able to took a lot of lables/classes as supplementary input.
+The model the presented is a conditional model which was able to take a lot of lables/classes as supplementary input.
 They were able to create highly different sample spaces at a time.
-Unlike CGAN, the discriminator in this case learnt the supplementary information on its own, this technique is referred as reconstruction loss.
+Unlike CGAN, the discriminator, in this case, learnt the supplementary information on its own, this technique is referred to as reconstruction loss.
 
@@
 InfoGAN is a GAN which utilises the information shared among a subset of the latent space.
-It also uses an unsupervised learning technique called disentagled representation which allocated different sets of dimensions by breaking down features of the data.
+It also uses an unsupervised learning technique called disentangled representation which allocated different sets of dimensions by breaking down features of the data.
 Disentangled information represents a low representation of the data.
-With the introdcution of this technique, it makes the model to be truly unsupervised.
-InfoGAN as claimed by the authors contributes comparatively less computation cost when used with GAN also making it easier to train.
-
-\subsubsection{PacGAN}
-
-\subsubsection{Pix2PixGAN}
-
-\subsubsection{Cycle-GAN}
-
-\subsubsection{Text-to-Image Synthesis (StackGAN)}
-
-\subsubsection{Super-Resolution GAN}
+With the introduction of this technique, it makes the model truly unsupervised.
+InfoGAN, as claimed by the authors, contributes comparatively less computation cost when used with GAN also making it easier to train.
 
@@
 Autoencoders are a type of neural networks which learns in an unsupervised way.
-As the name suggests, it encodes the input and then try to reconstruct the input to generate a similar or better output.
-This way it learns to reduce unnecassary features while being able to produce the same input data it was fed.
+As the name suggests, it encodes the input and then tries to reconstruct the input to generate similar or better output.
+This way it learns to reduce unnecessary features while being able to produce the same input data it was fed.
 This technique is often used for dimension reduction, fix noisy data, or compression without losing significant parts of the data.
@@
 
-In the above figure \ref{fig4}, an autencoder is shown.
-It has 2 main components: an encoder which takes in the input and encodes it and a decoder which uses the encoded output of the encoder as input and tries to generate the original input of the model.
+In the above figure \ref{fig4}, an autoencoder is shown.
+It has 2 main components: an encoder which takes in the input and encodes it and a decoder which uses the encoded output of the encoder as an input and tries to generate the original input of the model.
 Due to the backpropagation nature of this model, the training is quite fast.
@@
 Variational Autoencoders (VAEs) are generative models.
-It is based on vanilla autencoders but with a distinct property of picking up input from a latent space which is continous in nature.
-It basically avoids overfitting by regularizing its training.
+It is based on vanilla autoencoders but with a distinct property of picking up input from a continuous latent space.
+It avoids overfitting by regularizing its training.
 Unlike GAN, where a discriminator is used to classify the data which in turn helps the generator to tune itself to fool the discriminator, VAEs learn how to generate the data.
@@
 This enables the model to generate distinct samples with similar characteristics to the input.
-VAEs can work with an surprisingly diverse data forms, continous or discrete, labelled or unlabelled, sequential or non-sequential, making it an extremely efficient generative learning technique.
+VAEs can work with a surprisingly diverse data forms, continuous or discrete, labelled or unlabelled, sequential or non-sequential, making it an extremely efficient generative learning technique.
 VAEs has proven to produce images out of latent space but it often performs poorly.
@@
 \label{conclusion}
+This review paper has covered a brief review on generative learning in computer vision focusing more towards GANs.
+It has been noted that GANs was introduced as a basic architecture and computer scientists have built upon different variants of GANs on this original GAN.
+Some GANs performed the same thing but with better accuracy as compared to others with novel architectural changes like DCGAN and Conditional GAN, while some GANs did different tasks like 3D-GAN and StackGAN.
+These variants of GANs has proved to be a starting point for other GANs like 3D-GAN is based on the architecture of DCGAN.
+The paper has also shown the inefficient generative method being used before GANs were introduced, Variational Autoencoders.
+A brief overview of autoencoders and how VAEs are different from autoencoders was also presented.
+The generative methods presented in this paper are not exhaustive, more methods have been presented and proposed by researchers in this field.
+The paper has covered some popular methods used in the CV.
+Currently, GANs have proved to be a major break-through in generative learning, it is not hard to say that GANs will be around for a while and many such researchers will not stop innovating over this model.
 
